TBD

### 2024-04-07 outputs/paper/paper.qmd
paper updated

# Generating fake data for average house prices for each US state
set.seed(42) # For reproducibility
states <- map_data("state")$region %>% unique()
average_house_prices <- runif(n = length(states), min = 100000, max = 700000)
state_average_prices <- data.frame(State = states, AverageHousePrice = average_house_prices)

>>>>

# Generating fake data for average house prices for each US state
set.seed(123) # For reproducibility
states <- map_data("state")$region %>% unique()
average_house_prices <- runif(n = length(states), min = 100000, max = 700000)
state_average_prices <- data.frame(State = states, AverageHousePrice = average_house_prices)
